TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-10-20 paper/draft.tex
HOGG notes

\color{gcolor}{Some note on what lines vary significantly with parameter...}\color{black}

@@

To obtain visual band magnitudes for a set of sources, we cross-matched the 10,311 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,000 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:aspcap_cannon_validation} shows the temperature validation tests for each of the three relations and compared to the \aspcap\ temperatures for the same sources. \color{gcolor}{Comments about validation results and the uncertainty of our Cannon temperatures...}\color{black}

@@

\item[-] Some discussion of whether the derivatives are sensible or surprising.

\item[-] \thecannon\ as a test of evaluating training parameter accuracy?

\item[-] Discussion of validation tests and ground truth

\item[-] HOGG: Discussion of the implications of these results for the NASA \tess\ Mission and how the future might change..?
\end{enumerate}

Future work:
\begin{enumerate}
\item[-] Create a binary sample; using color/magnitude \citealt{Widmark:2018} and by spectroscopy \citealt{ElBadry:2018}
\end{enumerate}

>>>>

\color{gcolor}{HOGG/ADAM: Do we want some note on what lines vary significantly with parameter? I could summarize the which kinds of lines show increasing or decreasing trends, but have no idea how to interpret from there.}\color{black}

@@

To obtain visual band magnitudes for a set of sources, we cross-matched the 10,311 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,000 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:teff_comparisons} shows the temperature validation tests for each of the three relations and compared to the \aspcap\ temperatures for the same sources. \color{gcolor}{Comments about validation results and the uncertainty of our Cannon temperatures...}\color{black}

@@

\item[-] Some discussion of whether the derivatives are sensible or surprising. \color{gcolor}{HOGG: I'm not sure what to say here}\color{black}

\item[-] \color{gcolor}{HOGG:\thecannon\ as a test of evaluating training parameter accuracy?}\color{black}

\item[-] \color{gcolor}{HOGG: Discussion of validation tests and ground truth}\color{black}

\end{enumerate}

Future work:
\begin{enumerate}
\item[-] Create a binary sample; using color/magnitude \citealt{Widmark:2018} and by spectroscopy \citealt{ElBadry:2018}

\item[-] \color{gcolor}{HOGG: Discussion of the implications of these results for the NASA \tess\ Mission and how the future might change..?}\color{black}
\end{enumerate}

\color{gcolor}{HOGG: Is a conclusion section necessary?}\color{black}
